### 2019-09-30 management.tex
bachman edits

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{ncreid2.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Diversity Co-Chair - Nathan Reid}$\\
	Nate graduated with a B.S. in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016. He is a 4th-year Ph.D. student in the field of fusion and plasma science and engineering under Prof. Jean Paul Allain. Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working in the nuclear structural materials group under the mentorship of Dr. Lauren Garrison. Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting. Nate has been recognized by the ANS-UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President. He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend. Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.
\end{minipage}

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-chee.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Technical Subcommittee Chair - Gwen Chee}$\\
	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr. Kathryn Huff in the ARFC group. Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.She also serves as the president of the UIUC chapter of Women In Nuclear (WiN). Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019. She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
\end{minipage}

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.  will be supplied by either UIUC ANS members or students of the NPRE department. While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events. If not, we will rely on other student organizations for support including, but not limited to: ACDIS and WIE. Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter. Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels. Thus, it will be an overall positive experience for the volunteers. Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.

>>>>

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{ncreid2.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Diversity Co-Chair - Nathan Reid}$\\
	Nate graduated with a B.S. in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016. He is a 4th-year Ph.D. student in the field of fusion and plasma science and engineering under Prof. Jean Paul Allain. Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working in the nuclear structural materials group under the mentorship of Dr. Lauren Garrison. He will return the UIUC in December 2019. Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting. Nate has been recognized by the ANS-UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President. He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend. Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.
\end{minipage}

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-chee.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Technical Subcommittee Chair - Gwen Chee}$\\
	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr. Kathryn Huff in the ARFC group. Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex. She also serves as the president of the UIUC chapter of Women In Nuclear (WIN). Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019. She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
\end{minipage}

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.  will be supplied by either UIUC ANS members or students of the NPRE department. While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events. If not, we will rely on other student organizations for support including, but not limited to: Arms Control and Domestic and International Security (ACDIS) and Women in Engineering (WIE). Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter. Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels. Thus, it will be an overall positive experience for the volunteers. Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.

### 2019-09-30 proglog.tex
bachman edits

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-baranwal.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Dr. Rita Baranwal serves as the Assistant Secretary for the Office of Nuclear Energy in the U.S. Department of Energy (DOE).  Dr. Baranwal leads the office’s efforts to promote research and development (R$\&$D) on existing and advanced nuclear technologies that sustain the existing U.S. fleet of nuclear reactors, enable the deployment of advanced nuclear energy systems, and enhance the U.S.A.'s global commercial nuclear energy competitiveness. Prior to her current role, Dr. Baranwal directed the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative at Idaho National Laboratory.  She was responsible for providing the nuclear industry and other stakeholders access to DOE's state-of-the-art R$\&$D expertise, capabilities, and infrastructure to achieve faster and cost-effective development, demonstration, and ultimate deployment of innovative nuclear energy technologies. Under her leadership, GAIN positively impacted over 120 companies. Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.
\end{minipage}

@@

\subsubsection{Suzanne Hobbs Baker}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-baker.jpeg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals. Baker has a strong track record as a nuclear science communicator. In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy. She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy. Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference. Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
\end{minipage}

@@

% \clearpage
\subsubsection{Jim Conca, Forbes}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-conca.jpeg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals. He is a Trustee of the Herbert M. Parker Foundation, Adjunct at WSU, an Affiliate Scientist at LANL and consult on strategic planning for the DOE, EPA/State environmental agencies, and industry including companies that own nuclear, hydro, wind farms, large solar arrays, coal and gas plants. He also writes for Forbes magazine about nuclear issues, energy, and the environment. Conca has a strong vision for the future and is not shy about coming up with ideas to solve grand challenge problems. In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike. Together, these factors make him an ideal speaker at the conference.
\end{minipage}

@@

\subsubsection{Building Your Network}
The AAAS conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future. They hold regular workshops about strategic networking, making new contacts, and getting the most out of a conference. We will invite them to conduct a workshop where attendees can come away with skills to maximize their experience at the ANS Student Conference.

@@

\subsubsection{PyNE and PyRK Workshop}
Python for Nuclear Engineering (PyNE) and Python for Reactor Kinetics (PyRK) are two open source packages with computational tools for nuclear science and engineering. The PyNE toolkit provides both a Python and a C++ API for common computational pre- and post-processing tasks in nuclear engineering. PyRK offers point kinetics implementation for nuclear reactors. This workshop will provide a hands-on tutorial for attendees to begin using PyNE and make use of its capabilities for their curriculum and research work. The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors. This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills. The workshop will be approximately two hours of instruction at NCSA room 1030.

>>>>

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-baranwal.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Dr. Rita Baranwal serves as the Assistant Secretary for the Office of Nuclear Energy in the U.S. Department of Energy (DOE).  Dr. Baranwal leads the office’s efforts to promote research and development (R$\&$D) on existing and advanced nuclear technologies that sustain the existing U.S. fleet of nuclear reactors, enable the deployment of advanced nuclear energy systems, and enhance the U.S.A.'s global commercial nuclear energy competitiveness. Prior to her current role, Dr. Baranwal directed the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative at Idaho National Laboratory.  She was responsible for providing the nuclear industry and other stakeholders access to DOE's state-of-the-art R$\&$D expertise, capabilities, and infrastructure to achieve faster and cost-effective development, demonstration, and ultimate deployment of innovative nuclear energy technologies. Under her leadership, GAIN positively impacted over 120 companies. Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology. We would ask her to give a call to action for students on the final night of the conference.
\end{minipage}

@@

\subsubsection{Suzanne Hobbs Baker}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-baker.jpeg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals. Baker has a strong track record as a nuclear science communicator. In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy. She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy. Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference. Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience. Thus she would be a great speaker on the opening night.
\end{minipage}

@@

% \clearpage
\subsubsection{Jim Conca, Forbes}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-conca.jpeg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals. He is a Trustee of the Herbert M. Parker Foundation, Adjunct at WSU, an Affiliate Scientist at LANL and consult on strategic planning for the DOE, EPA/State environmental agencies, and industry including companies that own nuclear, hydro, wind farms, large solar arrays, coal and gas plants. He also writes for Forbes magazine about nuclear issues, energy, and the environment. Conca has a strong vision for the future and is not shy about coming up with ideas to solve grand challenge problems. In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike. His diverse background makes him an ideal speaker to discuss the importance of developing a diverse network on the second night of the conference.
\end{minipage}

@@

\subsubsection{Building Your Network}
The American Association for the Advancement of Science (AAAS) conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future. They hold regular workshops about strategic networking, making new contacts, and getting the most out of a conference. We will invite them to conduct a workshop where attendees can come away with skills to maximize their experience at the ANS Student Conference.

@@

\subsubsection{PyNE and PyRK Workshop}
Python for Nuclear Engineering (PyNE) and Python for Reactor Kinetics (PyRK) are two open source packages with computational tools for nuclear science and engineering. The PyNE toolkit provides both a Python and a C++ API for common computational pre- and post-processing tasks in nuclear engineering. PyRK offers point kinetics implementation for nuclear reactors. This workshop will provide a hands-on tutorial for attendees to begin using PyNE and make use of its capabilities for their curriculum and research work. The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors. This workshop, tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills. The workshop will be approximately two hours of instruction at NCSA room 1030.

### 2019-09-30 socials.tex
adds farm lake pics
bachman edits

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.

% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}		
\end{figure}

\subsubsection{77 Club at Memorial Stadium}
Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field. The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange. This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet. This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall). Tables will be set up around a stage featuring live music and a dance floor and drinks will be served. This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!

% 77 Club Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{77club1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{77club2.png}
	\end{subfigure}		
\end{figure}

\subsubsection{Pour Bros. Taproom in Downtown Champaign}
Welcome to Illinois' first pour-your-own taprooms. Pour Bros. Taproom is located in the heart of the historic downtown Champaign area and features 28 pour-your-own taps: beers, ciders, meads and wine\ldots all poured by you, one ounce at a time. Socialize over the vintage games Pour Bros has to offer: skeeball, bubble hockey, steel tip darts, DAGZ and more! If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.

% Pour Bros Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
	\end{subfigure}		
\end{figure}

\subsubsection{Under 21 Social: University of Illinois Ice Arena}
For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.

% Ice Arena Picture
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ice_arena.png}
\end{figure}

>>>>

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

\subsubsection{77 Club at Memorial Stadium}
Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field. The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange. This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet. This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall). Tables will be set up around a stage featuring live music and a dance floor and drinks will be served. This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing! 
\vspace{0.5cm}\newline
% 77 Club Picture
\begin{figure}[H]

	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{77club1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{77club2.png}
	\end{subfigure}
	\caption{77 Club at Memorial Stadium}		
\end{figure}

%% Reserve for Pour Bros. social %%%
\subsubsection{Pour Bros. Taproom in Downtown Champaign}
Welcome to Illinois' first pour-your-own taprooms. Pour Bros. Taproom is located in the heart of the historic downtown Champaign area and features 28 pour-your-own taps: beers, ciders, meads and wine\ldots all poured by you, one ounce at a time. Socialize over the vintage games Pour Bros has to offer: skeeball, bubble hockey, steel tip darts, DAGZ and more! If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
\vspace{0.5cm}\newline
% Pour Bros Picture
\begin{figure}[H]

	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
	\end{subfigure}	
	\caption{Pour Brothers Taproom}	
\end{figure}

\subsubsection{Barn Dance: A Proud Midwestern Tradition}
Barn dances are a staple event at UIUC. Socialize in a unique environment with games of corn-hole and other midwestern fun. Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually. Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service. Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor! 
\vspace{0.5cm}\newline
% Barn Dance Hudson Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
	\end{subfigure}%
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
	\end{subfigure}	
	\caption{Hudson Farm Barn.}	
\end{figure} 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
	\end{subfigure}%
	\begin{subfigure}{0.4\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
	\end{subfigure}	
	\caption{Farm Lake Barn}	
\end{figure}

\subsubsection{Under 21 Social: University of Illinois Ice Arena}
For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.
\vspace{0.5cm}\newline
% Ice Arena Picture
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ice_arena.png}
	\caption{The UIUC Ice Arena}
\end{figure}
